\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.72in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{enumitem}

\definecolor{primary}{HTML}{0F4C5C}
\definecolor{textmain}{HTML}{1F2933}
\definecolor{textmuted}{HTML}{5B6470}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.25em}
\setlist[itemize]{leftmargin=1.2em, itemsep=0.2em, topsep=0.2em, parsep=0em, partopsep=0em}
\renewcommand{\labelitemi}{\textcolor{primary}{\small$\bullet$}}

\newcommand{\cvsection}[1]{
  \vspace{0.7em}
  {\large\textbf{\textcolor{primary}{\textsc{#1}}}}\\[-0.35em]
  {\color{primary}\rule{\linewidth}{0.8pt}}
  \vspace{0.15em}
}

\newcommand{\cvjob}[4]{
  \begin{tabularx}{\linewidth}{@{}Xr@{}}
    \textbf{#1} & \textcolor{textmuted}{#2}\\
    \textit{#3} & \textit{\textcolor{textmuted}{#4}}
  \end{tabularx}
}

\newcommand{\tightitems}{
  \setlength{\itemsep}{0.1em}
  \setlength{\parskip}{0em}
  \setlength{\parsep}{0em}
}

\begin{document}
\color{textmain}

{\Huge\textbf{\textcolor{primary}{Ra\'ul Beltr\'an G\'omez}}}\\[-0.15em]
{\small \textcolor{textmuted}{Madrid, Spain (Spanish Citizenship) \textbar{} +34 642 58 15 03 \textbar{} rb58853@gmail.com}}\\
{\small
\href{https://github.com/rb58853}{github.com/rb58853}
\textcolor{textmuted}{\ \textbar\ }
\href{https://portfolio.rb58853.net}{portfolio.rb58853.net}
\textcolor{textmuted}{\ \textbar\ }
\href{https://www.linkedin.com/in/rb58853/}{linkedin.com/in/rb58853}}

\vspace{0.2em}
{\color{primary}\rule{\linewidth}{1pt}}

\cvsection{Professional Summary}
Backend and AI developer with experience building production systems with MCP, LLMs, NLP, and REST APIs. Strong background in chatbot architecture, secure integrations, and Unity/Python cross-stack development for real products.

\cvsection{Experience}
\cvjob{Cogitia}{Madrid, Spain (Remote for Barcelona, Spain)}{MCP, LLM, Chatbot and REST API Developer}{14/05/2025 -- 24/04/2026}
\begin{itemize}
  \tightitems
  \item Designed and maintained MCP servers for enterprise workflows using embedded LLM clients and robust prompt/tool/resource patterns.
  \item Implemented secure authentication flows (OAuth 2.1 and header-based auth) and scalable integrations with internal systems.
  \item Built NLP-driven modules for business automation, including data operations, scheduling, and internal query handling.
\end{itemize}

\cvjob{Word Games}{Havana, Cuba (Remote for Bogot\'a, Colombia)}{Game Developer, Development Team}{20/10/2024 -- 10/05/2025}
\begin{itemize}
  \tightitems
  \item Led end-to-end programming of Arcane Ascent (deck-building roguelike) and shipped the title on Steam Early Access.
  \item Integrated native Steam systems (achievements and saves), improving platform readiness and user experience.
  \item Developed an automated language-generation pipeline using NLP + OpenAI, with JSON-based Python--Unity interoperability.
\end{itemize}

\cvjob{Devman}{Havana, Cuba (Remote for Madrid, Spain)}{NLP, Chatbot and REST API Developer}{10/04/2024 -- 14/10/2024}
\begin{itemize}
  \tightitems
  \item Architected an e-commerce assistant combining NLP intent handling and product retrieval for faster discovery.
  \item Built backend services in FastAPI, including API key security, WebSocket chat, and authorization layers.
\end{itemize}

\cvsection{Education}
\textbf{University of Havana} \hfill Havana, Cuba\\
\textit{Bachelor of Computer Science} \hfill Expected 23/01/2024
\vspace{0.15em}
\begin{itemize}
  \tightitems
  \item Relevant study fields: Artificial Intelligence and Machine Learning, Information Retrieval Systems, Compilers, Operating Systems, Databases, Distributed Systems, Networks, Data Structures and Algorithms, Design and Analysis of Algorithms, Graph Theory, Number Theory.
\end{itemize}

\cvsection{Skills}
\textbf{Languages:} Spanish (native), English (B1).\\
\textbf{Programming:} Python, C\#, C/C++, JavaScript, Assembly (MIPS).\\
\textbf{Technical:} MCP, LLMs, NLP, RAG, FastAPI, TensorFlow, PyTorch, .NET, Databases, ReactJS, Unity Engine.

\end{document}
